A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2025-01-07 manuscript/manuscript.qmd
formatting

Causal analyses of observational data may not have the same pre-requisites in terms of formal hypothesis testing and statistical power than RCTs since the number of 'recruited' patients is given and cannot be influenced.[@hernan2022causal] For this project, however, the emulations in EHR data must have at least equal power to the relevant trial for interpretation of the pre-specified agreements metrics between RCT and RWD results. Since the main outcome of interest is defined as time to all-cause mortality (OS), the estimation of the statistical power is driven by the number of events rather than the number of patients. To assess if the unstratified number of events is sufficient such that a significant difference can be detected based on the original RCT-reported hazard ratio (HR), the statistical power $\beta$ will be estimated using Schoenfeld's sample-size formula for the proportional-hazards regression model.\[@schoenfeld1981asymp\]

>>>>

Causal analyses of observational data may not have the same pre-requisites in terms of formal hypothesis testing and statistical power than RCTs since the number of 'recruited' patients is given and cannot be influenced.[@hernan2022causal] For this project, however, the emulations in EHR data must have at least equal power to the relevant trial for interpretation of the pre-specified agreements metrics between RCT and RWD results. Since the main outcome of interest is defined as time to all-cause mortality (OS), the estimation of the statistical power is driven by the number of events rather than the number of patients. To assess if the unstratified number of events is sufficient such that a significant difference can be detected based on the original RCT-reported hazard ratio (HR), the statistical power $\beta$ will be estimated using Schoenfeld's sample-size formula for the proportional-hazards regression model.[@schoenfeld1981asymp]
